---
output: 
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# SVP: Efficient analysis of 'gene set' activity in spatial or single-cell data

```{r, echo=FALSE, results="hide", message=FALSE}
library(badger)
```

## :newspaper: Description

```{r, comment="", echo=FALSE, results='asis'}
cat(packageDescription('SVP')$Description)
```

## :writing_hand: Author

[Shuangbin Xu](https://github.com/xiangpin) and [Guangchuang Yu](https://guangchuangyu.github.io)

School of Basic Medical Sciences, Southern Medical University

## :arrow_double_down: Installation

The development version from `github`:

```r
if (!requireNamespace("remotes", quietly=TRUE))
    install.packages("remotes")
remotes::install_github("xiangpin/SVP")
```

To enhance performance, it is **strongly recommended** to connect your R BLAS library with the 
[OpenBLAS](https://github.com/OpenMathLib/OpenBLAS) library for matrix calculations.
This can be accomplished using the [ropenblas](https://prdm0.github.io/ropenblas/) package.
Or you can install [OpenBLAS](https://github.com/OpenMathLib/OpenBLAS) and link the library 
to R BLAS library by `ln -s your_openblas_installed_path_libopenblas.so your_R_install_path_libRblas.so`
manually.

## :sparkling_heart: Contributing

We welcome any contributions! By participating in this project you agree to abide
by the terms outlined in the [Contributor Code of Conduct](CONDUCT.md).
